\documentclass{article}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Hout Tang}
\date{March 30, 2022}

\begin{document}


\maketitle

\section*{Summary 1}
% First summary: 
There are several reasons why JavaScript Mobile App Development Framework is the best pick in 2022.The first reason is that majority of developer are familiar with developing apps using JavaScript. Hence, it saves lot of time on learning.\cite{AparnaArticle}. the second reason is that many top tech companies such as Google and Facebook are using JavaScript framework for their mobile app development. Some of the best JavaScript Framework are React Native, jQuery, Ionic ,Apache Cordova and AngularJS.\cite{AparnaArticle}.




%used to skip line 
\medskip

\section*{Summary 2}
% Second summary: 

Android and iOS are two of the biggest app development platform in the world.There are several important comparison between those two platform .\cite{DanielArticle}. The first comparison is The app marketplace security. The best winner is iOS. The reason is that apple closely inspects every app on its app store while android's play store is more open source and it imposes to many possible hacking opportunities for hackers. The second comparison is updating to patch vulnerabilities. Apple update are more easier to control across any devices and promising consistent security while android devices has to serve makes it impossible to keep all of the devices updated to the same level of security \cite{DanielArticle}.


\printbibliography

\end{document}
