\documentclass{article}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Hout Tang}
\date{April 6, 2022}

\begin{document}


\maketitle

\section*{Summary 1}
% First summary: 
Blockchain technology has become very popular and many tech industries have been impacted by its usage\cite{BCArticle}. The blockchain technology support digital currency such as bitcon and ethereum, which enables a very secure and transparent payment process. On top of that it is very beneficial for mobile developers.There are several reason why it is useful. The first reason is that, it offers increased data security. Due to its decentralized architecture, the risk of third party app cause chaos is less. The second reason is that blockchain provides a high reliability for mobile application as it has robust and reliable infrastructure.\cite{BCArticle}.

 

%used to skip line 
\medskip

\section*{Summary 2}
% Second summary: 

Agile development refer to the ability to create and respond to change. In software development point of view, it is the term for a set of frameworks and practices based on the principles and values.\cite{AgileArticleg}. Moreover, Agile development also refer to many development processes which aligned with the idea of Agile Manifesto.The reason why software development teams need Agile is that Agile encourages ideas of team, promotes improvements among teams and empowers the team members. \cite{al2020agile}. 




\printbibliography

\end{document}
