\documentclass{article}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Hout Tang}
\date{February 28, 2022}

\begin{document}


\maketitle

\section*{Summary 1}
% First summary: 

There are five main benefit of using GitHub.  \cite{ApiumhubpArticle}. The first benefit is that GitHub will make it easy for every developer to contribute to open source projects. It has several useful features which allows developer to fork a project, make modification and send a pull request. The second benefit is documentation. GitHub allows users to document their project easily. The third benefit is that it is the best place to showcase software projects. Majority of developer could use GitHub to show the recruiters what have they done for their projects. The fourth benefit is that it is the best platform to track the modification of developers' code.The final benefit is that GitHub could be integrated with other platforms such as google cloud and amazon. \cite{ChandramohanJagtapArticle}.


%used to skip line 
\medskip

\section*{Summary 2}
% Second summary: 

There are 7 phases of software development life cycle. The first stage is project planning. In this stage, the developers try to answer the question "What do we want ?". The second phase is that gathering requirements and analysis. In this stage, developers need to gather as much information as they could from clients. Then they start accessing and analysing the requirements and come up with design and codes.The main goal in this stage is to make sure every team member understand the requirements \cite{BetsolArticle}. The third stage is design, which matches the clients requirements. Once the design is finalized, the developer will design the use of program languages \cite{BetsolArticle}.The fourth stage is implementation of code. The developers have to follow certain predefined coding guidelines and tools such as compilers tools.The fifth stage is testing. After building the software, developers will start testing the code and ensure that the entire applications works based on the clients requirement. The sixth stage is deployment. it is when developers release the products to client. On top of that, developers will also need to provide documentations that help client to operate the software. The final stage is maintenance. As long as the software start working. the issues will occur accordingly. The developer will need to solve the problem from time to time. In other word, the software will need to be updated timely \cite{BetsolArticle}.


\printbibliography

\end{document}
