\documentclass{article}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Hout Tang}
\date{February 23, 2022}

\begin{document}


\maketitle

\section*{Summary 1}
% First summary: 

There are five major reasons why iOS development is so popular. The first reason is that iOS development jobs are increasing in demand. Approximately 1.5 millions jobs were created since 2008 \cite{ddArticle}. On top of that, iOS app generated a new economy that worth more than 1.3 trillion US dollars as of Feb 2021.The second reason is that Apple's programming language is easier to learn. Swift programming language is known as structured and limited. With it restrictions, it means that programmers are less likely to get off track when developing app.The third reason is that iOS development tools are more sophisticated. Apple's IDE is considered as world-class since it is easy to use , stable and user-friendly.\cite{ddArticle}.The final reason is that iOS has amazing opportunities and community which is supportive \cite{digiteArticle}.  

%used to skip line 
\medskip

\section*{Summary 2}
% Second summary: Introduction to Bitcoin and Block-chain

The idea of block-chain came up in October 2008. As part of the proposal for Bitcoin. Its purpose is to create P2P money without banks \cite{ChandramohanJagtapArticle}.In addition, bitcoin network is consisted of a big number of computers or nodes. Each of those node has its own copy of bitcoin block-chain. Moreover, bitcoin offers a low transaction fee if compared to any regular payment gateways. Block-chain's system comprised of transaction, personal identification, banking, immutable ledgers, decentralized nodes, encryption processes and smart contracts \cite{ChandramohanJagtapArticle}


\printbibliography

\end{document}
