\documentclass{article}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Hout Tang}
\date{February 2022}

\begin{document}


\maketitle

\section*{Summary 1}
% First summary: Involvement of Artificial Intelligence in Mobile Applications 
Artificial Intelligence is a significant technology which has revolutionized the technology world. According to emizentech website, it estimates that AI software market revenue will reach approximately 70.94 billion US dollars by 2023 \cite{nagarArticle}
 .We could easily find artificial intelligence implements in major technological products. For instance, we could find the AI technology is used in smart phones applications which includes speech recognition, image recognition, face detection, image classification. The main reason why AI technology is so popular is that AI enhances both users and developers experiences. From users’ point of view, AI offers a user-friendly and smooth experience. From developers’ point of view, AI technology enables the developers to make prediction on users’ behaviors and offer a recommendations or improve or update the mobile applications for users. 




%used to skip line 
\medskip

\section*{Summary 2}
% Second summary: Influence of Covid-19 on Mobile App Development Market

Covid-19 pandemic has shifted people’ lives and daily routines. Due to lockdown and many restrictions, people need to find other ways to stay socialized. Covid-19 has accelerated the demand of mobile applications. Some businesses such as restaurants or grocery stores needed to update or add user-friendly app to their businesses to cope with demand. As a result, the mobile app development market had increased exponentially \cite{medini2020ramping}. “According to a report by SensorTower Website, the Covid-19 pandemic has led to the 52 percentages increase in data usage due to the increased downloading of mobile applications \cite{TkaArticle}. However, the mobile development during pandemic also cause many issues. One of the most concerning issues is the data security concerns. As many developers worked from homes or from remote locations. The risk of data security had been increased since those data might be the target of cybercriminals \cite{medini2020ramping}.





\printbibliography

\end{document}
